### 2014-08-31 fundamentals/impl.tex
spelling
moved the modified open figure to the implementation section.

@@

Cycamore contains a number of usefule facility models that are a mere base-set.
Additional modules are needed for interesting fuel cycle simulation. However,
simple, once-through fuel cycles can be generated with Cycamore and Cyclus alone.

>>>>

Additionally, the clean plug-in architecture loads modules without any
modifications to the \Cyclus kernel. Thus, as in Figure \ref{fig:modifiedopen},
closed-source archetypes can be used with the simulator alongside open-source
archetypes. This architecture therefore allows closed-source libraries (e.g.,
those representing sensitive nuclear processes and subject to export control)
to be developed and used privately.

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations.}
\label{fig:modifiedopen}
\end{figure}

@@

Cycamore contains a number of useful facility models that are a mere base-set.
Additional modules are needed for interesting fuel cycle simulation. However,
simple, once-through fuel cycles can be generated with Cycamore and Cyclus alone.
